Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-25 paper/main.tex
Added results for last 2 months

>>>>

\section{Findings}

\subsection{Deification of our method}
\begin{itemize}
	\item we built protein function and ontology based features based on DL2vec
	\item Ontology derived protein function focused features are highly predictive for dtis
	\item We built a versatile template for various features to test localization on the PPI graph
	\item normal GCNs don't work on PPI graph, as it is highly connected $\rightarrow$ needs stronger more expressive aggregation function $\rightarrow$ GENConv in residual blocks for better numerical stability
	\item protein functions localize on the PPI graph, while molecular features don't
	\item all AUROC in \% AUROC score on STITCH

	\begin{tabular}{|l|r|r|}
		\hline
		DNNT model&Without graph model&With graph model\\
		\hline
		MolPred&$69$&$69$\\
		PhenomeNETPred&$88$&$92$\\
		\hline
		MolPred + PhenomeNETPred & $89$ & $93$\\
		\hline
	\end{tabular}
	\item microAUC for MolPred + PhenomeNETPred on graph is about $93+-$
	\item and on yamanishi dataset

	\begin{tabular}{|l|r|r|}
		\hline
		DNNT model&Without graph model&With graph model\\
		\hline
		PhenomeNETPred&$83$&$84$\\
		\hline
		MolPred + PhenomeNETPred & $83$ & $84.5$\\
		\hline
	\end{tabular}
	\item MicroAUC is about $83$
\end{itemize}

\subsection{How to insult other methods}
\begin{itemize}
	\item Only few other methods perform their split over proteins \citep{Survey2018}, DTI-CDF does it
	\item Running split over proteins is harder than, drug and drug protein pair split (see below table)
	\item this applies for both DTI prediction and drug target affinity prediction (and Saras gene-disease association)
	\item using indications is like cheating, as not applicable for searching new drugs
	\item drug indications are highly predictive for downstream tasks, but lack capability to differentiate highly related drugs/proteins
	\item Stratified Cross validation is suitable for training, but \textbf{NOT} for validating and testing (Uselessly high AUPRC)
	\item microAUC is a superior and more intuitive metric for drug repurposing $\rightarrow$ why for each protein and not for each drug

	\begin{tabular}{|l|l|r|r|r|}
		\hline
		Approach&Splitting scheme&Original AUROC score&Protein split AUROC&MicroAUC\\
		\hline
		DTINet&DP pairs&$91$&$84.1$&$67.2$\\
		DTIGEMS+&DP pairs&$93$& $72.2$& $67.8$ \\
		DTI-CDF&Proteins&$83$&$83$&$79$\\
		GNN-DTI&&&&\\
		\hline
		MolTrans&&&&\\
		GraphData&&&&\\
		\hline
	\end{tabular}
	\item A naive predictor (ranking proteins) and predict each drug similarly achieves cutting edge performance ($87.5$ AUROC for whole dataset, $85.5$ for 5-fold cross validation in drug-split) $\rightarrow$ No prot focused microAUC possible. $\rightarrow$ hub proteins
	\item Yamanishi Dataset is only partially suitable, if everybody just derives a suitable subset (DTIGEMS)
\end{itemize}
